|                                   |
|-----------------------------------|
| title: "class 3 counts and stuff" |
| author: "anhad"                   |

Setup chunk:

```{r}
library(tidyverse)
library(mosaic)
library(ggformula)
library(skimr)
library(kableExtra)
```

## Taxi dataset

```{r}
taxi <- read_csv("https://vincentarelbundock.github.io/Rdatasets/csv/modeldata/taxi.csv")
taxi
```

### Inspecting the dataset

```{r}
glimpse(taxi)
```

```{r}
skim(taxi) %>% kbl()
```

```{r}
inspect(taxi)
```

### Mutating the dataset

```{r}
## Convert `dow`, `local`, and `month` into ordered factors
taxi_modified <- taxi %>%
  mutate(
    dow = factor(dow,
      levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
      labels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
      ordered = TRUE
    ),
    ##
    local = factor(local,
      levels = c("no", "yes"),
      labels = c("no", "yes"),
      ordered = TRUE
    ),
    ##
    month = factor(month,
      levels = c("Jan", "Feb", "Mar", "Apr"),
      labels = c("Jan", "Feb", "Mar", "Apr"),
      ordered = TRUE
    )
  )
taxi_modified %>% glimpse()
```

### Q1. Do people tip or not?

```{r}

gf_bar(~ tip, data = taxi_modified) %>%
  gf_labs(title = "Plot A: Counts of Tips")

ggplot(taxi_modified)  + 
  geom_bar(aes(x = tip)) + 
  labs(title = "Plot 1A: Counts of Tips")
```

#### Inferences are

Most people tip :)

### Q2. Does the tip depend on whether the trip is local or not?

```{r}
taxi_modified %>% 
  gf_bar(~ local, fill = ~ tip, position = "dodge") %>% 
  gf_labs(title = "Dodged Bar Chart")
##
taxi_modified %>% 
  gf_bar(~ local, fill = ~ tip, position = "stack") %>% 
  gf_labs(title = "Stacked Bar Chart",
          subtitle = "Can we spot per group differences in proportions??")

## Showing "per capita" percentages
taxi_modified %>% 
  gf_bar(~ local, fill = ~ tip, position = "fill") %>% 
  gf_labs(title = " Filled Bar Chart",
          subtitle = "Shows Per group differences in Proportions!")
## Showing "per capita" percentages
## Better labelling of Y-axis
taxi_modified %>% 
  gf_props(~ local, fill = ~ tip, position = "fill") %>% 
  gf_labs(title = " Filled Bar Chart",
          subtitle = "Shows Per group differences in Proportions!")
```

#### Inferences are

Local cab services get paid less.

### Q3. Do some companies get more tips than others?

```{r}

taxi_modified %>% 
  gf_bar(~ company, color = ~ tip, position = "dodge") %>% 
  gf_labs(title = "Plot 2A: Dodged Bar Chart") %>% 
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
##
taxi_modified %>% 
  gf_bar(~ company, fill = ~ tip, position = "stack") %>% 
  gf_labs(title = "Plot 2B: Stacked Bar Chart",
          subtitle = "Can we spot per group differences in proportions??") %>% 
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
## Showing "per capita" percentages
taxi_modified %>% 
  gf_bar(~ company, fill = ~ tip, position = "fill") %>% 
  gf_labs(title = "Plot 2C: Filled Bar Chart",
          subtitle = "Shows Per group differences in Proportions!") %>% 
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
## Showing "per capita" percentages
## Better labelling of Y-axis
taxi_modified %>% 
  gf_props(~ company, fill = ~ tip, position = "fill") %>% 
  gf_labs(title = "Plot 2D: Filled Bar Chart",
          subtitle = "Shows Per group differences in Proportions!") %>% 
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

```         
```

#### Inferences are

Yes, other companies are paid more, followed by Taxi Affiliation Services.

```{r}
taxi_modified %>% 
  gf_bar(~ local, fill = ~ tip, position = "dodge") %>% 
  gf_labs(title = "Dodged Bar Chart")
##
taxi_modified %>% 
  gf_bar(~ local, fill = ~ tip, position = "stack") %>% 
  gf_labs(title = "Stacked Bar Chart",
          subtitle = "Can we spot per group differences in proportions??")

## Showing "per capita" percentages
taxi_modified %>% 
  gf_bar(~ local, fill = ~ tip, position = "fill") %>% 
  gf_labs(title = " Filled Bar Chart",
          subtitle = "Shows Per group differences in Proportions!")
## Showing "per capita" percentages
## Better labelling of Y-axis
taxi_modified %>% 
  gf_props(~ local, fill = ~ tip, position = "fill") %>% 
  gf_labs(title = " Filled Bar Chart",
          subtitle = "Shows Per group differences in Proportions!")
```

### 

```         
```

### Q4. Does a tip depend on the distance, hour, day of week and month?

```{r}
gf_bar(~ tip,fill = ~local, data = taxi_modified, position = "dodge",) %>%
  gf_labs(title = "Plot A: Counts of Tips")

gf_bar(~ hour, fill = ~ tip, data = taxi_modified) %>%
  gf_labs(title = "Plot B: Counts of Tips by Hour")
##
gf_bar(~ dow, fill = ~ tip, data = taxi_modified) %>%
  gf_labs(title = "Plot C: Counts of Tips by Day of Week")
##
gf_bar(~ month, fill = ~ tip, data = taxi_modified) %>%
  gf_labs(title = "Plot D: Counts of Tips by Month")

##
gf_bar(~ month | dow, fill = ~ tip, data = taxi_modified) %>%
  gf_labs(title = "Plot E: Counts of Tips by Day of Week and Month")
##
## This may be too busy a graph...
gf_bar(~ dow | hour, fill = ~ tip, data = taxi_modified) %>%
  gf_labs(title = "Plot F: Counts of Tips by Hour and Day of Week",
          subtitle = "Is this plot arrangement easy to grasp?")
## This is better!
gf_bar(~ hour | dow, fill = ~ tip, data = taxi) %>%
  gf_labs(title = "Plot G: Counts of Tips by Hour and Day of Week",
          subtitle = "Swapped the Facets")
```

#### Inferences are

People tip most at 04:00PM and least at 03:00AM.

People tip most on Thursdays and least on Sundays.

People tip most in the month of April and least in the month of January.

The highest chance of getting a good tip is on Wednesdays and Thursdays in March, and the lowest chance is a Sunday in January.

```         
```

## My turn (Apartments dataset)

```{r}
apartments <- read_delim("../../posts/data/apartments.csv")
apartments
ggplot(apartments, aes(x = GrLivArea, y = SalePrice)) +
  geom_point() +
  labs(title = "Sale Price vs. Ground Living Area",
       x = "Ground Living Area (sq ft)",
       y = "Sale Price ($)") +
  theme_minimal()
ggplot(apartments, aes(x = SalePrice)) +
  geom_histogram(binwidth = 10000, fill = "blue", color = "black") +
  labs(title = "Distribution of Sale Prices",
       x = "Sale Price ($)",
       y = "Frequency") +
  theme_minimal()


```

```{r}
inspect(apartments)
```

```{r}
glimpse(apartments)
```

```{r}
skim(apartments)
```

#### Inferences

The highest price is 345,000 but it the ground live area is 2324, and the highest grlivearea is 2376 but the price is 325300.

```{r}
library(dplyr)

# Read the CSV file
apartments <- read_delim("apartments.csv")

# Mutate the dataset by adding a new column
apartments <- apartments %>%
  mutate(PricePerSqFt = SalePrice / GrLiveArea)

# Save the mutated dataset back to a CSV file (optional)
write.csv(apartments, "mutated_apartments.csv", row.names = FALSE)

```

Data doesn't need to be mutated since it's not qualitative data.

```         
```

```         
```
