---
title: "Summaries"
author: "Anhad"
editor: 
  markdown: 
    wrap: 72
---

The ***skim*** function is to get a rough idea of the data - a literal
skim.

```{r}
skimr::skim(mpg) 
```

Here's our data - showing the first 10 entries.

```{r}
mpg %>% 
  head(10)
```

Here's a ***glimpse*** of our dataset.

```{r}
glimpse(mpg)
```

***Inspecting*** the data gives us a slightly more detailed summary
compared to glimpse.

```{r}
inspect(mpg)
```

## Intro

## This is our classwork on summarizing data.

Setup chunk:

```{r}
#| label: setup
library(tidyverse)
library(ggformula)
library(mosaic)
library(kableExtra)
library(babynames)
```

### Data:

```{r}
mpg %>%
  head(10) %>%
  kbl(
    # add Human Readable column names
    col.names = c(
      "Manufacturer", "Model", "Engine\nDisplacement",
      "Model\n Year", "Cylinders", "Transmission",
      "Drivetrain", "City\n Mileage", "Highway\n Mileage",
      "Fuel", "Class\nOf\nVehicle"
    ),
    caption = "MPG Dataset"
  ) %>%
  kable_styling(
    bootstrap_options = c(
      "striped", "hover",
      "condensed", "responsive"
    ),
    full_width = F, position = "center"
  )
```

### Mutating

```{r}
mpg_modified <- mpg %>%
  dplyr::mutate(
    cyl = as_factor(cyl),
    fl = as_factor(fl),
    drv = as_factor(drv),
    class = as_factor(class),
    trans = as_factor(trans)
  )
glimpse(mpg_modified)
```

### Counts

```{r}
mpg_modified %>% dplyr::count(cyl)
```

```{r}
mpg_modified %>% mosaic::count(drv) # does the same thing! Counts!
```

```{r}
mpg_modified %>% count(fl)
```

```{r}
### All combinations of cut, color, clarity
### Overwhelming??
mpg_modified %>%
  count(across(where(is.factor)))
```

### Finding out the averages

```{r}
mpg_modified %>%
  group_by(cyl) %>%
  summarize(average_hwy = mean(hwy), count = n())
```

```{r}
mpg_modified %>%
  group_by(cyl, fl) %>%
  summarize(average_hwy = mean(hwy), count = n())
```

Skim output for mpg dataset

```{r}
skimr::skim(mpg) %>%
  kbl(align = "c", caption = "Skim Output for mpg Dataset") %>%
  kable_paper(full_width = F)
```

# My turn (Math anxiety dataset)

```{r}
math_anxiety <- read_delim("../../data/MathAnxiety.csv")
math_anxiety
```

### Finding averages based on types of anxiety

```{r}
math_anxiety %>% 
  group_by(Gender) %>% 
  summarise(average_AMAS=mean(AMAS), count=n())
```

```{r}
math_anxiety %>% 
  group_by(Gender) %>% 
  summarise(average_RCMAS=mean(RCMAS), count=n())

```

### Summarizing Math anxiety data

```{r}
skimr::skim(math_anxiety)

```

```{r}
inspect(math_anxiety)

```

```{r}
glimpse(math_anxiety)

```

### Mutating and summarizing the dataset

```{r}
math_anxiety_modified <- math_anxiety %>%
  dplyr::mutate(
    Gender = as_factor(Gender),
    Grade = as_factor(Grade),
    )

glimpse(math_anxiety_modified)

```

```{r}
math_anxiety_modified %>% dplyr::count(Gender)

```

```{r}
math_anxiety_modified %>% mosaic::count(Grade) 

```

```{r}
math_anxiety_modified %>%
  count(across(where(is.factor)))

```

```{r}
math_anxiety %>%
  head(10) %>%
  kbl(
    col.names = c(
      "Age", "Gender", "Grade",
      "AMAS Score", "RCMAS Score", "Arithmetic Score"
    ),
    longtable = FALSE, centering = TRUE,
    caption = "Math Anxiety Dataset"
  ) %>%
  kable_styling(
    bootstrap_options = c(
      "striped", "hover",
      "condensed", "responsive"
    ),
    full_width = FALSE, position="center"
)
```
